A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.

### 2022-04-18 inst/manuscript/supporting.tex
minor review updates

SRS-DB & Gridded & Normal & 0\% & 50 & 0.0004 & 0.1922 & 0.9345 \\ 

@@

  GRTS-MB & Gridded & Normal & 0\% & 50 & -0.0112 & 0.1905 & 0.9490 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 50 & 0.0004 & 0.1965 & 0.8955 \\ 

@@

  GRTS-MB & Gridded & Skewed & 0\% & 50 & -0.0048 & 0.1988 & 0.9110 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

SRS-DB & Random & Normal & 0\% & 50 & -0.0002 & 0.1964 & 0.9295 \\ 

@@

  GRTS-MB & Random & Normal & 0\% & 50 & 0.0031 & 0.1940 & 0.9425 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

SRS-DB & Random & Skewed & 0\% & 50 & 0.0016 & 0.1941 & 0.8985 \\ 

@@

  GRTS-MB & Random & Skewed & 0\% & 50 & 0.0000 & 0.1861 & 0.9225 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

SRS-DB & Gridded & Normal & 50\% & 50 & -0.0031 & 0.1472 & 0.9400 \\ 

@@

  GRTS-MB & Gridded & Normal & 50\% & 50 & -0.0013 & 0.1775 & 0.9460 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 50 & -0.0060 & 0.1605 & 0.9085 \\ 

@@

  GRTS-MB & Gridded & Skewed & 50\% & 50 & -0.0047 & 0.1891 & 0.9100 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

SRS-DB & Random & Normal & 50\% & 50 & -0.0097 & 0.1507 & 0.9315 \\ 

@@

  GRTS-MB & Random & Normal & 50\% & 50 & 0.0061 & 0.1744 & 0.9445 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

SRS-DB & Random & Skewed & 50\% & 50 & -0.0021 & 0.1624 & 0.9000 \\ 

@@

  GRTS-MB & Random & Skewed & 50\% & 50 & 0.0014 & 0.1804 & 0.9195 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

SRS-DB & Gridded & Normal & 90\% & 50 & -0.0037 & 0.0960 & 0.9400 \\ 

@@

  GRTS-MB & Gridded & Normal & 90\% & 50 & 0.0055 & 0.1621 & 0.9355 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 50 & -0.0039 & 0.1039 & 0.9205 \\ 

@@

  GRTS-MB & Gridded & Skewed & 90\% & 50 & 0.0007 & 0.1546 & 0.9345 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

SRS-DB & Random & Normal & 90\% & 50 & -0.0011 & 0.0940 & 0.9410 \\ 

@@

  GRTS-MB & Random & Normal & 90\% & 50 & 0.0058 & 0.1575 & 0.9470 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

SRS-DB & Random & Skewed & 90\% & 50 & -0.0026 & 0.1127 & 0.9225 \\ 

@@

  GRTS-MB & Random & Skewed & 90\% & 50 & -0.0022 & 0.1772 & 0.9305 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

SRS-DB & Gridded & Normal & 0\% & 100 & -0.0010 & 0.1352 & 0.9445 \\ 

@@

  GRTS-MB & Gridded & Normal & 0\% & 100 & -0.0028 & 0.1352 & 0.9475 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 100 & 0.0077 & 0.1307 & 0.9155 \\ 

@@

  GRTS-MB & Gridded & Skewed & 0\% & 100 & -0.0001 & 0.1384 & 0.9210 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

SRS-DB & Random & Normal & 0\% & 100 & 0.0019 & 0.1318 & 0.9460 \\ 

@@

  GRTS-MB & Random & Normal & 0\% & 100 & -0.0004 & 0.1339 & 0.9450 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

SRS-DB & Random & Skewed & 0\% & 100 & 0.0039 & 0.1315 & 0.9230 \\ 

@@

  GRTS-MB & Random & Skewed & 0\% & 100 & 0.0021 & 0.1322 & 0.9280 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

SRS-DB & Gridded & Normal & 50\% & 100 & -0.0003 & 0.0993 & 0.9435 \\ 

@@

  GRTS-MB & Gridded & Normal & 50\% & 100 & -0.0025 & 0.1207 & 0.9420 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 100 & -0.0019 & 0.1127 & 0.9175 \\ 

@@

  GRTS-MB & Gridded & Skewed & 50\% & 100 & 0.0023 & 0.1221 & 0.9315 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

SRS-DB & Random & Normal & 50\% & 100 & -0.0010 & 0.0997 & 0.9380 \\ 

@@

  GRTS-MB & Random & Normal & 50\% & 100 & -0.0016 & 0.1214 & 0.9440 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

@@

SRS-DB & Random & Skewed & 50\% & 100 & -0.0002 & 0.1105 & 0.9235 \\ 

@@

  GRTS-MB & Random & Skewed & 50\% & 100 & 0.0020 & 0.1188 & 0.9395 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 20.} 

@@

SRS-DB & Gridded & Normal & 90\% & 100 & -0.0013 & 0.0602 & 0.9425 \\ 

@@

  GRTS-MB & Gridded & Normal & 90\% & 100 & -0.0027 & 0.1083 & 0.9460 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 21.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 100 & 0.0004 & 0.0695 & 0.9280 \\ 

@@

  GRTS-MB & Gridded & Skewed & 90\% & 100 & -0.0015 & 0.1108 & 0.9345 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 22.} 

@@

SRS-DB & Random & Normal & 90\% & 100 & -0.0007 & 0.0570 & 0.9480 \\ 

@@

  GRTS-MB & Random & Normal & 90\% & 100 & 0.0002 & 0.1071 & 0.9490 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 23.} 

@@

SRS-DB & Random & Skewed & 90\% & 100 & 0.0023 & 0.0671 & 0.9230 \\ 

@@

  GRTS-MB & Random & Skewed & 90\% & 100 & -0.0019 & 0.1165 & 0.9325 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 24.} 

@@

SRS-DB & Gridded & Normal & 0\% & 200 & 0.0032 & 0.0843 & 0.9610 \\ 

@@

  GRTS-MB & Gridded & Normal & 0\% & 200 & 0.0005 & 0.0891 & 0.9465 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 25.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 200 & 0.0005 & 0.0892 & 0.9405 \\ 

@@

  GRTS-MB & Gridded & Skewed & 0\% & 200 & -0.0018 & 0.0894 & 0.9440 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 26.} 

@@

SRS-DB & Random & Normal & 0\% & 200 & 0.0009 & 0.0882 & 0.9480 \\ 

@@

  GRTS-MB & Random & Normal & 0\% & 200 & 0.0019 & 0.0905 & 0.9385 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 27.} 

@@

SRS-DB & Random & Skewed & 0\% & 200 & -0.0011 & 0.0873 & 0.9395 \\ 

@@

  GRTS-MB & Random & Skewed & 0\% & 200 & 0.0007 & 0.0867 & 0.9400 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 28.} 

@@

SRS-DB & Gridded & Normal & 50\% & 200 & 0.0039 & 0.0679 & 0.9375 \\ 

@@

  GRTS-MB & Gridded & Normal & 50\% & 200 & -0.0016 & 0.0777 & 0.9520 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 29.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 200 & 0.0018 & 0.0691 & 0.9360 \\ 

@@

  GRTS-MB & Gridded & Skewed & 50\% & 200 & 0.0013 & 0.0816 & 0.9400 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 30.} 

@@

SRS-DB & Random & Normal & 50\% & 200 & 0.0009 & 0.0643 & 0.9510 \\ 

@@

  GRTS-MB & Random & Normal & 50\% & 200 & 0.0008 & 0.0816 & 0.9389 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 31.} 

@@

SRS-DB & Random & Skewed & 50\% & 200 & -0.0007 & 0.0679 & 0.9385 \\ 

@@

  GRTS-MB & Random & Skewed & 50\% & 200 & -0.0041 & 0.0789 & 0.9510 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 32.} 

@@

SRS-DB & Gridded & Normal & 90\% & 200 & -0.0008 & 0.0376 & 0.9475 \\ 

@@

  GRTS-MB & Gridded & Normal & 90\% & 200 & -0.0011 & 0.0730 & 0.9450 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 33.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 200 & 0.0010 & 0.0423 & 0.9375 \\ 

@@

  GRTS-MB & Gridded & Skewed & 90\% & 200 & 0.0038 & 0.0768 & 0.9430 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 34.} 

@@

SRS-DB & Random & Normal & 90\% & 200 & 0.0014 & 0.0368 & 0.9475 \\ 

@@

  GRTS-MB & Random & Normal & 90\% & 200 & 0.0026 & 0.0713 & 0.9495 \\ 

@@

SRS-DB & Random & Skewed & 90\% & 200 & -0.0001 & 0.0396 & 0.9419 \\ 

>>>>

SRS-DB & Gridded & Normal & 0\% & 50 & -0.0112 & 0.1905 & 0.9490 \\ 

@@

  GRTS-MB & Gridded & Normal & 0\% & 50 & 0.0004 & 0.1922 & 0.9345 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 50 & -0.0048 & 0.1988 & 0.9110 \\ 

@@

  GRTS-MB & Gridded & Skewed & 0\% & 50 & 0.0004 & 0.1965 & 0.8955 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

SRS-DB & Random & Normal & 0\% & 50 & 0.0031 & 0.1940 & 0.9425 \\ 

@@

  GRTS-MB & Random & Normal & 0\% & 50 & -0.0002 & 0.1964 & 0.9295 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

SRS-DB & Random & Skewed & 0\% & 50 & 0.0000 & 0.1861 & 0.9225 \\ 

@@

  GRTS-MB & Random & Skewed & 0\% & 50 & 0.0016 & 0.1941 & 0.8985 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

SRS-DB & Gridded & Normal & 50\% & 50 & -0.0013 & 0.1775 & 0.9460 \\ 

@@

  GRTS-MB & Gridded & Normal & 50\% & 50 & -0.0031 & 0.1472 & 0.9400 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 50 & -0.0047 & 0.1891 & 0.9100 \\ 

@@

  GRTS-MB & Gridded & Skewed & 50\% & 50 & -0.0060 & 0.1605 & 0.9085 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

SRS-DB & Random & Normal & 50\% & 50 & 0.0061 & 0.1744 & 0.9445 \\ 

@@

  GRTS-MB & Random & Normal & 50\% & 50 & -0.0097 & 0.1507 & 0.9315 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

SRS-DB & Random & Skewed & 50\% & 50 & 0.0014 & 0.1804 & 0.9195 \\ 

@@

  GRTS-MB & Random & Skewed & 50\% & 50 & -0.0021 & 0.1624 & 0.9000 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

SRS-DB & Gridded & Normal & 90\% & 50 & 0.0055 & 0.1621 & 0.9355 \\ 

@@

  GRTS-MB & Gridded & Normal & 90\% & 50 & -0.0037 & 0.0960 & 0.9400 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 50 & 0.0007 & 0.1546 & 0.9345 \\ 

@@

  GRTS-MB & Gridded & Skewed & 90\% & 50 & -0.0039 & 0.1039 & 0.9205 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

SRS-DB & Random & Normal & 90\% & 50 & 0.0058 & 0.1575 & 0.9470 \\ 

@@

  GRTS-MB & Random & Normal & 90\% & 50 & -0.0011 & 0.0940 & 0.9410 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

SRS-DB & Random & Skewed & 90\% & 50 & -0.0022 & 0.1772 & 0.9305 \\ 

@@

  GRTS-MB & Random & Skewed & 90\% & 50 & -0.0026 & 0.1127 & 0.9225 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

SRS-DB & Gridded & Normal & 0\% & 100 & -0.0028 & 0.1352 & 0.9475 \\ 

@@

  GRTS-MB & Gridded & Normal & 0\% & 100 & -0.0010 & 0.1352 & 0.9445 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 100 & -0.0001 & 0.1384 & 0.9210 \\ 

@@

  GRTS-MB & Gridded & Skewed & 0\% & 100 & 0.0077 & 0.1307 & 0.9155 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

SRS-DB & Random & Normal & 0\% & 100 & -0.0004 & 0.1339 & 0.9450 \\ 

@@

  GRTS-MB & Random & Normal & 0\% & 100 & 0.0019 & 0.1318 & 0.9460 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

SRS-DB & Random & Skewed & 0\% & 100 & 0.0021 & 0.1322 & 0.9280 \\ 

@@

  GRTS-MB & Random & Skewed & 0\% & 100 & 0.0039 & 0.1315 & 0.9230 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

SRS-DB & Gridded & Normal & 50\% & 100 & -0.0025 & 0.1207 & 0.9420 \\ 

@@

  GRTS-MB & Gridded & Normal & 50\% & 100 & -0.0003 & 0.0993 & 0.9435 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 100 & 0.0023 & 0.1221 & 0.9315 \\ 

@@

  GRTS-MB & Gridded & Skewed & 50\% & 100 & -0.0019 & 0.1127 & 0.9175 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

SRS-DB & Random & Normal & 50\% & 100 & -0.0016 & 0.1214 & 0.9440 \\ 

@@

  GRTS-MB & Random & Normal & 50\% & 100 & -0.0010 & 0.0997 & 0.9380 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

@@

SRS-DB & Random & Skewed & 50\% & 100 & 0.0020 & 0.1188 & 0.9395 \\ 

@@

  GRTS-MB & Random & Skewed & 50\% & 100 & -0.0002 & 0.1105 & 0.9235 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 20.} 

@@

SRS-DB & Gridded & Normal & 90\% & 100 & -0.0027 & 0.1083 & 0.9460 \\ 

@@

  GRTS-MB & Gridded & Normal & 90\% & 100 & -0.0013 & 0.0602 & 0.9425 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 21.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 100 & -0.0015 & 0.1108 & 0.9345 \\ 

@@

  GRTS-MB & Gridded & Skewed & 90\% & 100 & 0.0004 & 0.0695 & 0.9280 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 22.} 

@@

SRS-DB & Random & Normal & 90\% & 100 & 0.0002 & 0.1071 & 0.9490 \\ 

@@

  GRTS-MB & Random & Normal & 90\% & 100 & -0.0007 & 0.0570 & 0.9480 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 23.} 

@@

SRS-DB & Random & Skewed & 90\% & 100 & -0.0019 & 0.1165 & 0.9325 \\ 

@@

  GRTS-MB & Random & Skewed & 90\% & 100 & 0.0023 & 0.0671 & 0.9230 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 24.} 

@@

SRS-DB & Gridded & Normal & 0\% & 200 & 0.0005 & 0.0891 & 0.9465 \\ 

@@

  GRTS-MB & Gridded & Normal & 0\% & 200 & 0.0032 & 0.0843 & 0.9610 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 25.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 200 & -0.0018 & 0.0894 & 0.9440 \\ 

@@

  GRTS-MB & Gridded & Skewed & 0\% & 200 & 0.0005 & 0.0892 & 0.9405 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 26.} 

@@

SRS-DB & Random & Normal & 0\% & 200 & 0.0019 & 0.0905 & 0.9385 \\ 

@@

  GRTS-MB & Random & Normal & 0\% & 200 & 0.0009 & 0.0882 & 0.9480 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 27.} 

@@

SRS-DB & Random & Skewed & 0\% & 200 & 0.0007 & 0.0867 & 0.9400 \\ 

@@

  GRTS-MB & Random & Skewed & 0\% & 200 & -0.0011 & 0.0873 & 0.9395 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 28.} 

@@

SRS-DB & Gridded & Normal & 50\% & 200 & -0.0016 & 0.0777 & 0.9520 \\ 

@@

  GRTS-MB & Gridded & Normal & 50\% & 200 & 0.0039 & 0.0679 & 0.9375 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 29.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 200 & 0.0013 & 0.0816 & 0.9400 \\ 

@@

  GRTS-MB & Gridded & Skewed & 50\% & 200 & 0.0018 & 0.0691 & 0.9360 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 30.} 

@@

SRS-DB & Random & Normal & 50\% & 200 & 0.0008 & 0.0816 & 0.9389 \\ 

@@

  GRTS-MB & Random & Normal & 50\% & 200 & 0.0009 & 0.0643 & 0.9510 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 31.} 

@@

SRS-DB & Random & Skewed & 50\% & 200 & -0.0041 & 0.0789 & 0.9510 \\ 

@@

  GRTS-MB & Random & Skewed & 50\% & 200 & -0.0007 & 0.0679 & 0.9385 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 32.} 

@@

SRS-DB & Gridded & Normal & 90\% & 200 & -0.0011 & 0.0730 & 0.9450 \\ 

@@

  GRTS-MB & Gridded & Normal & 90\% & 200 & -0.0008 & 0.0376 & 0.9475 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 33.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 200 & 0.0038 & 0.0768 & 0.9430 \\ 

@@

  GRTS-MB & Gridded & Skewed & 90\% & 200 & 0.0010 & 0.0423 & 0.9375 \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 34.} 

@@

SRS-DB & Random & Normal & 90\% & 200 & 0.0026 & 0.0713 & 0.9495 \\ 

@@

  GRTS-MB & Random & Normal & 90\% & 200 & 0.0014 & 0.0368 & 0.9475 \\ 

@@

SRS-DB & Random & Skewed & 90\% & 200 & 0.0028 & 0.0708 & 0.9504 \\ 
